---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# readeba


<!-- badges: start -->
[![R-CMD-check](https://github.com/MattCowgill/readeba/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/MattCowgill/readeba/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of `{readeba}` is to download and import [data on enterprise agreement settlements in Australia from the Fair Work Commission](https://www.fwc.gov.au/agreements-awards/enterprise-agreements/about-enterprise-agreements/statistical-reports-enterprise?idU=1).

## Installation

You can install the development version of readeba from [GitHub](https://github.com/) with:


``` r
# install.packages("devtools")
devtools::install_github("MattCowgill/readeba")
```

## Examples!

The package has one function: `read_fwc()`, which downloads and imports a tidy tibble containing the FWC EBA data

```{r example}
library(readeba)
options(tidyverse.quiet = TRUE)
library(tidyverse)

fwc <- read_fwc()

fwc 
```

It's straightforward to visualise:


```{r}
fwc |> 
  filter(union == "Total",
         indicator == "AAWI (%)") |> 
  ggplot(aes(x = date, y = value)) +
  geom_line() +
  theme_minimal()
```

```{r}
fwc |> 
  filter(union == "Total") |> 
  pivot_wider(names_from = indicator) |> 
  ggplot(aes(x = date, 
             y = `AAWI (%)`,
             weight = `Employees covered (No.)` )) +
  geom_point(aes(size = `Employees covered (No.)`)) +
  geom_smooth(method = "loess",
              formula = y ~ x,
              se = FALSE) +
  scale_y_continuous(limits = \(x) c(0, x[2])) +
  scale_x_date(breaks = \(x) seq(x[2], x[1], by = "-6 months"))
```
