---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  fig.retina = 2,
  fig.dpi = 300
)
```

# readeba

<!-- badges: start -->

[![R-CMD-check](https://github.com/MattCowgill/readeba/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/MattCowgill/readeba/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

`{readeba}` helps you download and import [data on enterprise agreement settlements in Australia from the Fair Work Commission](https://www.fwc.gov.au/agreements-awards/enterprise-agreements/about-enterprise-agreements/statistical-reports-enterprise?idU=1).

## Installation

You can install `{readeba}` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("MattCowgill/readeba")
```

## Examples!

The package has one function: `read_fwc()`, which downloads and imports a tidy tibble containing the FWC EBA data

```{r example}
library(readeba)
library(dplyr)
library(ggplot2)
library(tidyr)

fwc <- read_fwc()

fwc 
```

It's straightforward to visualise!


```{r}
my_theme <- theme_minimal(base_size = 14) +
  theme(panel.grid.minor = element_blank(),
        axis.title = element_blank(),
        plot.caption.position = "plot",
        plot.title.position = "plot",
        plot.caption = element_text(size = rel(0.6), hjust = 0),
        legend.position = "bottom",
        legend.direction = "horizontal")


fwc |> 
  filter(union == "Total",
         indicator == "AAWI (%)") |> 
  ggplot(aes(x = date, y = value)) +
  geom_point() +
  geom_line() +
  scale_x_date(date_labels = "%d %b\n%Y",
               breaks = seq(max(fwc$date),
                            min(fwc$date),
                            "-6 months")) +
  scale_y_continuous(labels = \(x) paste0(x, "%"),
                     expand = expansion(0.1)) +
  my_theme +
  labs(subtitle = "Average annualised wage increase (AAWI)\nin newly-lodged enterprise agreements",
       caption = "Source: Fair Work Commission")
```

Add a couple of different trend lines:

```{r}
fwc |> 
  filter(union == "Total") |> 
  pivot_wider(names_from = indicator) |> 
  ggplot(aes(x = date, 
             y = `AAWI (%)`,
             weight = `Employees covered (No.)` )) +
  geom_point(aes(size = `Employees covered (No.)`),
             alpha = 0.2) +
  geomtextpath::geom_textsmooth(method = "loess",
                                label = "LOESS trend",
                                hjust = 0.1,
                                vjust = -0.2,
              formula = y ~ x,
              colour = "blue",
              se = FALSE) +
  geomtextpath::geom_textline(aes(y = slider::slide2_dbl(.x = `AAWI (%)`,
                                       .y = `Employees covered (No.)`,
                                       .f = \(x, y) weighted.mean(x, y),
                                       # 6 fortnight weighted moving average
                                       .before = 6L,
                                       .complete = TRUE)),
            na.rm = TRUE,
            label = "6 fortnight weighted moving average",
            text_smoothing = 40,
            hjust = 0.15,
            vjust = 1.2,
            colour = "red") +
  scale_x_date(breaks = seq(max(fwc$date), 
                            min(fwc$date), 
                            by = "-6 months"),
               date_labels = "%d %b\n%Y",
               expand = expansion(c(0.025, 0.075))) +
  scale_y_continuous(labels = \(x) paste0(x, "%"),
                     breaks = seq(0, 100, 1),
                     limits = \(x) c(min(0, x[1]), x[2]),
                     expand = expansion(c(0, 0.05))) +
  scale_size_continuous(labels = scales::comma) +
  my_theme +
  labs(subtitle = "Average annualised wage increase (AAWI)\nin newly-lodged enterprise agreements ",
       caption = "Source: Fair Work Commission")
```
